### 2018-05-05 papers/synth/experiments.tex
asd

\begin{table}[t]
  \centering
  \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}}\hline
    {\multirow{2}{*} \textbf{Size}}  & \multicolumn{2}{c|}{\textbf{Add edge}} & \multicolumn{2}{c|}{\textbf{Add molecules}} & \multicolumn{2}{c|}{\textbf{Low depth CNF}}  &  \multicolumn{2}{c|}{\textbf{Gate function}} &  \multicolumn{2}{c|}{\textbf{VTS repair}} \\\hline

   \cline{2-9}
    {} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} \\\hline

    plos1-dia[3/4C] & 0.0292 & $\infty$ & 0.0255 & $\infty$ & 0.0843 & $\infty$ & 0.1005 & $\infty$ & 0.0492 & 0.0\\\hline
    plos2-dia [4C] & 0.0414 & 0 & 0.0407 & 0 & 1.333 & 1 node & 2.327 & 1N 9PE & 0.042 & 0 \\\hline
%[M=8, N=2, Q=2]    
% n/A n/A activeN == UNSAT adding edge == UNSAT activeE == UNSAT presenceE == UNSAT
    mukund[3/4C] & 185.06 & 4N 8E & 0.3773 & 0.0 & 2.062 & 0.0 & !13.92/1.553 & 0.0 & 0.230 & 0.0 \\\hline
    node4[-] & 16.70 & 0.0 & 16.472 & 0.0 &  5.085 & $\infty$ & 7.011 & $\infty$ & 2.194 & 0.0\\\hline
    yeast-graph & 0.0 & 0.0 & 0.0 & 0.00 & 0.0 & 0.0 & 0.0  & 0.0 & 0.0 & 0.0 \\\hline
    mukund-comp & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0\\\hline
  \end{tabular}
  \caption{Run-times for searching for models (in secs). \#C  stands for minimum changes.
  Time is reported in seconds.}
  \label{tab:qf-graph}
\end{table}

@@

We have applied~\ourtool~on six partially defined VTSs.
%
The results are presented in table~\ref{tab:qf-graph}.
%
The experiments were conducted on a machine,
with \ashu{?}MHz processor, \ashu{?}GB memory, and 900s timeout.
%
The first four VTSs are synthetic, but inspire from literature for
typical motifs in VTSs. 
%
%
The fifth VTS is taken from "A complete set of SNAREs in yeast"
~\cite{burri2004complete} paper. It has been adapted from the paper by
separating the v and the t SNAREs. 
%The t SNAREs are labelled within compartments and v SNAREs on the edges. %\ashu{Describe the source of two examples}.
%
The last VTS represent mammalian SNARE map created by studying the literature references.

The table shows timing for various synthesis queries.
%
For each synthesis query, we have two columns.
%
One column reports the timing and the other reports the minimum changes
needed to obtain a valid VTS.
%
$\infty$ indicates that any number of changes with the synthesis query
search space can obtain the VTS.
%
%\ashu{@ankit: please discuss all the synthesis queries in the table.}

Variation 1 of our tool adds new labelled edges to the graph.
%
We have ranked the all possible graph edits with the simple rank of
minimum updates.
%
Our tools were able to complete this graph by adding five new edges
and nine new molecules in 210s.
%
Variation 2 of our graph adds new labels to the edge and was able to
fix this graph with eleven new molecule labels in 180s.
%
Variation 3 of our tool synthesis low depth CNF functions and was able
to synthesis the result in 500s.
%
Variation 4 of our tool synthesis Boolean function based on AND, OR
gates.
%
The result shows the basic template of 4 leaves and 3 gates we allow
the user to provide its own template in our front-end language.
%
The tool was able to synthesize the Boolean functions in 470s.
%
%
%Our experiments suggest that the synthesis problems are solvable by modern 
%solvers and the synthesis technology may be useful for biological research.
%

>>>>

\begin{table}[t]
  \centering
  \begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|}\hline
    {\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Learning NNF}}  &  \multicolumn{2}{c|}{\textbf{Learning}} &  \multicolumn{2}{c|}{\textbf{Add/Delete}} \\
    {\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
    \hline   
   \cline{2-9}
    {} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} \\\hline

    plos1-dia[3/4C]& 0.0292&$\infty$& 0.0255 &$\infty$& 0.1005      & $\infty$ & 0.0843&$\infty$& 0.0492 & 0.0\\\hline
    plos2-dia [4C] & 0.0414& 0      & 0.0407 & 0      & 2.327       & 1N 9PE   & 1.333 & 1 node & 0.042  & 0 \\\hline
    mukund[3/4C]  & 185.06 & 4N 8E  & 0.3773 & 0.0    & !13.92/1.553& 0.0      & 2.062 & 0.0    & 0.230  & 0.0 \\\hline
    node4[-]      & 16.70  & 0.0    & 16.472 & 0.0    & 7.011       & $\infty$ & 5.085 &$\infty$& 2.194  & 0.0\\\hline
    yeast-graph   & 0.0    & 0.0    & 0.0    & 0.00   & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0 \\\hline
    mukund-comp   & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
  \end{tabular}
  \caption{Run-times for searching for models (in secs). \#C  stands for minimum changes.
  Time is reported in seconds.}
  \label{tab:qf-graph}
\end{table}
%[M=8, N=2, Q=2]    
% n/A n/A activeN == UNSAT adding edge == UNSAT activeE == UNSAT presenceE == UNSAT

@@

We have applied~\ourtool~on six partially defined VTSs.
%
The results are presented in table~\ref{tab:qf-graph}.
%
The experiments were conducted on a machine,
with \ashu{?}MHz processor, \ashu{?}GB memory, and 900s timeout.
%
The first four VTSs are synthetic, but inspire from literature for
typical motifs in VTSs. 
%
%
The fifth VTS is taken from "A complete set of SNAREs in yeast"
~\cite{burri2004complete} paper. It has been adapted from the paper by
separating the v and the t SNAREs. 
%
The last VTS represent mammalian SNARE map created by studying the literature references.

The table shows timing for various synthesis queries.
%
For each synthesis query, we have two columns.
%
One column reports the timing and the other reports the minimum changes
needed to obtain a valid VTS.
%
$\infty$ indicates that any number of changes with the synthesis query
search space can obtain the VTS.
%
%\ashu{@ankit: please discuss all the synthesis queries in the table.}
In the table, we are reporting five synthesis queries
%
The first one only adds new labelled edges to the graph.
%
We have ranked the all possible graph edits with the simple rank of
minimum updates.
%
Our tools were able to complete the graphs by adding five new edges
and nine new molecules in 210s.
%
The second query adds new labels to the edge and was able to
fix the graphs with eleven new molecule labels in 180s.
%
The third query synthesizes NNF Boolean functions only containing
$\land$ and $\lor$ gates.
%
The result shows the basic template of 4 leaves and 3 gates we allow
the user to provide its own template in our front-end language.
%
The tool was able to synthesize the Boolean functions in 470s.
%
To illustrated the versatility of our tool,
the the fourth query synthesizes $3$-CNF functions (encoding not presented) and was able
to synthesis the results for all graphs in 500s.
%
Finally, we report queries that allows both addition and deletion of parts of
VTS\ashu{which parts}. 
%
%Our experiments suggest that the synthesis problems are solvable by modern 
%solvers and the synthesis technology may be useful for biological research.
%

### 2018-05-05 papers/synth/related.tex
still two ref to go
asd

In recent years, there has been a wide range of methods
developed for the similar synthesis problems~\cite{sketch,sygus,exampleSynth}.
%
They range from filling gaps an implementation of C programs from the
pool of template predicates to learn learn an a program from example
runs of the program.
%
In the course of developing such methods,
the background technology, i.e. solving of quantified
constraints,~\cite{lonsing2010depqbf,z3Quant} has been evolving rapidly.

There are a few examples of using synthesis technique in biology especially in gene regulatory networks~\cite{shavit2016automated, fisher2015synthesising}. A very recent work~\cite{fisher2015synthesising} synthesize executable gene regulatory networks from single-cell gene expression data. 
Synthesis technique is also used in optimal synthesis for chemical reaction networks~\cite{cardelli2017syntax}. The~\cite{fisher2015synthesising} uses constraint (satisfiability) solving techniques for the synthesis whereas ~\cite{shavit2016automated} uses SMT for synthesis. The paper~\cite{cardelli2017syntax} in addition of using SMT over ODE, uses a template-guided approach. In our case queries contain quantifiers so we have employed QBF solving with Z3 for the solving the synthesis problem. To our best knowledge this is the first application of synthesis in VTS.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

In recent years, there has been a wide range of methods
developed for the similar synthesis problems~\cite{sketch,sygus,exampleSynth}.
%
They range from filling gaps an implementation of C programs from the
pool of template predicates to learn learn an a program from example
runs of the program.
%
In the course of developing such methods,
the background technology, i.e. solving of quantified
constraints has been evolving rapidly~\cite{lonsing2010depqbf,z3Quant}.
%

There has been some work in
applying synthesis technique in biology especially in gene regulatory networks~\cite{shavit2016automated, fisher2015synthesising}. A very recent work~\cite{fisher2015synthesising} synthesize executable gene regulatory networks from single-cell gene expression data. 
Synthesis technique is also used in optimal synthesis for chemical reaction networks~\cite{cardelli2017syntax}. The~\cite{fisher2015synthesising} uses constraint (satisfiability) solving techniques for the synthesis whereas ~\cite{shavit2016automated} uses SMT for synthesis. The paper~\cite{cardelli2017syntax} in addition of using SMT over ODE, uses a template-guided approach. In our case queries contain quantifiers so we have employed QBF solving with Z3 for the solving the synthesis problem. To our best knowledge this is the first application of synthesis in VTS.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
